---
title: "Report Transformative Change Literature Search Chapter 2"
author: Rainer M Krug [Rainer.Krug@Senckenberg.de](mailto:Rainer.Krug@Senckenberg.de)
format:
    html:
        toc: true
        embed-resources: true
        code-fold: true
        code-summary: "Show the code"
    docx:
        toc: true
        number-sections: true
        highlight-style: github
    pdf:
        toc: true
        number-sections: true
params:
    s_tfc: '("transformative change" OR "deliberate transformation*" OR "transformative turn*" OR “transition*” OR “social-ecological change*” OR “deep change” OR “fundamental alteration” OR “profound change” OR “profound transformation” OR “radical transformation” OR “transformational change” OR “complete change” OR “complete transformation” OR “drastic change” OR “in-depth transformation” OR “progressive change” OR “radical alteration” OR “radical change” OR “revolutionary change” OR “significant modification” OR “total transformation” OR “transition” OR “pathway” OR “power” OR “agency” OR “scal*” OR “lever*” OR “context” OR “process” OR “regime” OR “shift” OR “views” OR “value*” OR “structure*” OR “institution*”or “deliberate” OR “structural” OR “fundamental” OR “system*” OR “deep” OR “radical” OR “profound” OR “drastic” OR “widespread” OR “politic*” OR “economic*” OR “structur*” OR “complete” OR “progressive” OR “revolutionary” OR “substanti*” OR “significan*”) AND (“transformati*” OR “alteration” OR  “change” OR “turn” OR “action” “transition” OR “shift”)'
    s_tfc_5: '("transformative change" OR "deliberate transformation*" OR "transformative turn*" OR "transition*” OR "social-ecological change*” OR "deep change" OR "fundamental alteration” OR "profound change” OR "profound transformation” OR "radical transformation” OR "transformational change” OR "complete change" OR "complete transformation” OR "drastic change” OR "in-depth transformation” OR "progressive change” OR "radical alteration” OR "radical change” OR "revolutionary change” OR "significant modification” OR "total transformation” OR "transformational shift” OR "radical shift”)'
    s_nat: '("sustainab*" OR "environ*" OR "resilien*" OR "conserv*" OR "biodivers*" OR “ecosystem*” OR “nature*” OR “planet*” OR “Earth” OR “biosphere”)' 
    s_nat_5:	("sustainab*" OR "environ*" OR "resilien*" OR "conserv*" OR "biodivers*" OR "ecosystem*” OR "nature*”)
    s_vis: '(“vision” OR “future” OR “visionar*”or “scenarios” OR “imagination” OR “imager*” OR “creativity” OR “desire”  OR “wish*” OR “visioning” OR “process” OR “participatory process*” OR “deliberate process*” OR “polic*” OR “target” OR  “view*” OR ”value” OR “cosmovision” OR  “cosmocentric” OR “dream*” OR “fiction” OR “hope” OR “mission” OR “objective” OR “story” OR “worldview*” OR “aspiration*” OR “action” OR “plan*” OR “strateg*” OR “intention” OR “model*” OR “solution*” OR  “innovation*” OR “perspective” OR “platform” OR “collective action” OR “cooperation” OR “consultation”or “coalition*” OR “response” OR “movement” OR “effort” OR “initiative” OR “activity” OR “reaction” OR “performance” OR “operation” OR “effect*” OR “task” OR “project” OR “influence” o “moment” OR “discourse” OR “motivation” OR “iteration” OR “roadmap” OR “agenda” OR “project” OR “programm” OR “government” OR “technique”  OR “inspiration” OR “culture” OR “universe*” OR “reality” OR “fantasy” OR “perception” OR “visualization” OR “approach” OR “image” OR “arquetype” OR “existence” OR “cosmolog*” OR “co-production” OR “knowledge” OR “dialogue” OR “transmission” OR “conceptual*” OR “ceremon*” OR “relationships” OR  “respect” OR “reciprocity” OR  “responsibilities” OR “solidarity” OR “harmony” OR “self-determination” OR “communit*” OR “spiritual*” OR “languague” OR “territory” OR “opportunit*” OR “sight” OR “foresight” OR “idea” OR “appearance”)'
---

```{r}
#| label: setup
#| include: false
#| 

if (!exists("params")){
    params <- rmarkdown::yaml_front_matter('~/Documents_Local/git/IPBES_data_tsu/Transformative Change/RMK - TFC Ch 2/Report.qmd')$params
}
library(openalexR)
library(knitr)
library(dplyr)
```

# Metadata

## Working Title
TfC Ch 2 Vision

## Contact Points

[Sebastian Villasante](mailto:s.villasante.arg@gmail.com)

## CC

[TfC tsu](mailto:ipbes-tsu-transformative-change@umontpellier.fr)

lynne.shannon@uct.ac.za
laurence.perianin@umontpellier.fr

aidin.niamir@senckenberg.de

## Data Online
[TODO Google Drive folder](https://drive.google.com/drive/folders/1IiALbIOAjYeL_IrlkZd-E7U7hr72iggx?usp=share_link)
### additional
- linked to in google folder https://docs.google.com/document/d/1WkuSySXbqag1qob37rhvoVrYtbpoGqa69EibD_x05GE/edit

## Code repo

[Github - private](https://github.com/rkrug/IPBES-TfC-Ch-2-Vision)

# Introduction

# Search Term Definition
## [About Transformative change] Transformative change synonyms
This should be aligned with TfC Ch 5 search

```{r}
params$s_tfc
``` 

This is the one from TfC Ch 5:

```{r}
params$s_tfc_5
```

## AND (nature synonyms) [use dictionary suggested by Aidin]
```{r}
params$s_nat
```

## AND (visions) [Ch 2 Key terms, https://www.ipbes.net/glossary-tag/vision, Oxford Dictionary]

```{r}
params$s_vis
```

## Final search terms

```{r}  
s_wos <- paste0("TS = ( ", params$s_tfc, " AND ", params$s_nat, " AND ", params$s_vis, " )")
s_oa  <- paste0(params$s_tfc, " AND ", params$s_nat, " AND ", params$s_vis)
```


# Results WoS

## R1

https://www.webofscience.com/wos/alldb/summary/9cc620dd-dfc6-4414-acc0-983d4a56314c-a1bdf5a4/relevance/1

1,237,718 hits

## R2

AND (“case stud*” OR “case” OR “study area*” OR “example*” OR “evaluation” OR “concrete” OR “empirical”, OR “practical” OR “initiative*”)

https://www.webofscience.com/wos/alldb/summary/f6d3094a-0cc2-4662-9b05-0a671c71c86a-a1be094a/relevance/1

296,551 hits, i.e. about 1,100,000 without case studies

# TODO

- Transformative Change Query term identical between chapters 2 and 5
- Nature Query terms identical between chapters between chapters 2 and 5
- 

- Randomly 100 papers from R1
- add large number of articles to Zotero
- all open acces articles only for now.

## R3
- get all pdfs which are available from R3
- Results, Discussion and Conclusion - Vision, geograph, country name, words from transformative change

# Look into translation into OpenAlex

# Results OpenAlex

## Transformative Change Ch 2
```{r}
hits <- rbind(
    openalexR::oa_query(search = params$s_tfc,)  |> oa_request(count_only = TRUE) |> unlist(),
    openalexR::oa_query(search = params$s_tfc_5) |> oa_request(count_only = TRUE) |> unlist(),  
    openalexR::oa_query(search = params$s_nat)   |> oa_request(count_only = TRUE) |> unlist(),
    openalexR::oa_query(search = params$s_nat_5) |> oa_request(count_only = TRUE) |> unlist(),    
    openalexR::oa_query(search = params$s_vis)   |> oa_request(count_only = TRUE) |> unlist(),
    openalexR::oa_query(
        search = paste0(
            "(", params$s_tfc, ")", " AND ",
            "(", params$s_nat, ")"
        )
    )  |>  oa_request(count_only = TRUE) |> unlist(),
    openalexR::oa_query(
        search = paste0(
            "(", params$s_nat, ")", " AND ",
            "(", params$s_vis, ")"
        )
    )  |>  oa_request(count_only = TRUE) |> unlist()
) |> 
    as.data.frame() |>
    mutate(query = c("Transform Ch", "Transform Ch 5", "Nature", "Nature Ch 5", "Visions", "TfC & Nature", "Nature & Vision")) |>
    mutate(page = NULL, per_page = NULL) |>
    mutate(count = formatC(count, format="f", big.mark=",", digits=0)) |>
    relocate(query, .before = count)

hits |>
    knitr::kable( 
        caption = "Number of hits",
    )
```

```{r}
openalexR::oa_query(
        search = paste0(
            "(", params$s_tfc, ")", " AND ",
            "(", params$s_nat, ")"
        )
    )  |>  
    oa_request(count_only = FALSE, verbose = TRUE) |>
    saveRDS(file = file.path(".", "tfc_nature.rds" )

openalexR::oa_query(
        search = paste0(
            "(", params$s_nat, ")", " AND ",
            "(", params$s_vis, ")"
        )
    )  |>  
    oa_request(count_only = FALSE, verbose = TRUE) |>
    saveRDS(file = file.path(".", "nature_vision.rds" )

```

```{r}
 openalexR::oa_query(
    title.search = params$s_tfc, 
    options = list(
        select = c("doi")
        )
    ) |> 
    oa_request(
        per_page = 200,
        count_only = FALSE, 
        verbose = TRUE
    )
 ```