---
title: 'Report Transformative Change Literature Search Chapter 2'
author: Rainer M Krug [Rainer.Krug@Senckenberg.de](mailto:Rainer.Krug@Senckenberg.de)
format:
    html:
        toc: true
        toc-depth: 5
        toc_expand: true
        embed-resources: true
        code-fold: true
        code-summary: 'Show the code'
params:

    # s_level_1: (transformation OR transition* OR ((shift OR change) AND (fundamental OR deep OR radical))) AND (socio OR social OR politics OR political OR governance OR economical OR cultural OR system* OR technological OR inner OR personal)  
    
    # s_tfc_rev: "('transformative change'  OR  'deliberate transformation*'  OR  'transformative turn*'  OR  'transition*'  OR  'social-ecological change*'  OR  'deep change'  OR  'fundamental alteration'  OR  'profound change'  OR  'profound transformation'  OR  'radical transformation'  OR  'transformational change'  OR  'complete change'  OR  'complete transformation'  OR  'drastic change'  OR  'in-depth transformation'  OR  'progressive change'  OR  'radical alteration'  OR  'radical change'  OR  'revolutionary change'  OR  'significant modification'  OR  'total transformation'  OR  'transition'  OR  'pathway'  OR  'power'  OR  'agency'  OR  'scale'  OR  'leverage'  OR  'context'  OR  'process'  OR  'regime'  OR  'shift'  OR  'views'  OR  'value*'  OR  'structure*'  OR  'institution*' OR  'deliberate'  OR  'structural'  OR  'fundamental'  OR  'system*'  OR  'deep'  OR  'radical'  OR  'profound'  OR  'drastic'  OR  'widespread'  OR  'political'  OR  'economical'  OR  'structur*'  OR  'complete'  OR  'progressive'  OR  'revolutionary'  OR  'substantial'  OR  'significant') AND ('transformation'  OR  'alteration'  OR  'change'  OR  'turn'  OR  'action' OR  'transition'  OR  'shift' )"
 
    s_1_oa: ""

    s_1_transformative_change: >-
      (
          (
              (
                  transformation
                  OR transition *
                  OR transformative
                  OR "transformative change"
              )
              OR (
                  (
                      shift
                      OR change
                  )
                  AND (
                      fundamental
                      OR deep
                      OR radical
                  )
              )
          )
          AND (
              socio
              OR social
              OR politics
              OR political
              OR governance
              OR economical
              OR cultural
              OR system *
              OR technological
              OR inner
              OR personal
          )
      )
      OR (
          (
              "transformative change"
              OR "deliberate transformation*"
              OR "transformative turn*"
              OR transition *
              OR "social-ecological change*"
              OR "deep change"
              OR "fundamental alteration"
              OR "profound change"
              OR "profound transformation"
              OR "radical transformation"
              OR "transformational change"
              OR "complete change"
              OR "complete transformation"
              OR "drastic change"
              OR "in-depth transformation"
              OR "progressive change"
              OR "radical alteration"
              OR "radical change"
              OR "revolutionary change"
              OR "significant modification"
              OR "total transformation"
              OR transition
              OR pathway
              OR power
              OR agency
              OR scale
              OR leverage
              OR context
              OR process
              OR regime
              OR shift
              OR views
              OR value *
              OR structure *
              OR institution *
              OR deliberate
              OR structural
              OR fundamental
              OR system *
              OR deep
              OR radical
              OR profound
              OR drastic
              OR widespread
              OR political
              OR economical
              OR structur *
              OR complete
              OR progressive
              OR revolutionary
              OR substantial
              OR significant
          )
          AND (
              transformation
              OR alteration
              OR change
              OR turn
              OR action
              OR transition
              OR shift
          )
      )

    s_1_nature_environment: >-
      biodiversity
      OR marine
      OR terrestrial
      OR forest*
      OR woodland*
      OR grassland*
      OR savanna*
      OR shrubland*
      OR peatland
      OR ecosystem*
      OR lake*
      OR river*
      OR sea
      OR ocean*
      OR meadow*
      OR heathland*
      OR mires
      OR bog*
      OR tundra
      OR biosphere
      OR desert*
      OR mountain*
      OR "natural resource*"
      OR estuary
      OR fjord*
      OR fauna
      OR flora
      OR soil*
      OR "coastal waters"
      OR wetland*
      OR freshwater
      OR marshland
      OR marches
      OR dryland*
      OR seascape*
      OR landscape*
      OR coast*
      OR "arable land*"
      OR "agricultural land*"
      OR "natural environment*"
      OR "environmental resource*"
      OR agroforest*
      OR "agro-forest*"
      OR plantation*
      OR "protected areas"
      OR chaparral
      OR sustainable
      OR environment
      OR resilience
      OR conservation
      OR ecosystem*
      OR nature*
      OR planet*
      OR Earth
      OR biosphere
      OR ecological
      OR "socio-ecological"
      OR restoration
      OR wildlife
      OR landscape
      OR species
      OR bioeconomy
      OR "resource system"
      OR "coupled system"
      OR nature

#    s_1_f_trans_nat: !expr function(){paste0("(", params$s_1_transformative_change, ") AND (", params$s_1_nature_environment, ")")}

    s_1_ch1_01: >-
      (
          root
          OR underlying
          OR indirect
      )
      AND (
          driver*
          OR cause*
      )

    s_1_ch1_02: >-
      equity
      OR inequity
      OR just*
      OR unjust*
      OR inequality
      OR equality
      OR Fair*
      OR unfair*

    s_1_ch1_03: >-
      scal*
      OR impact*
      OR leapfrog*
      OR transfer*

    s_1_ch1_04: >-
      inclusi*
      OR particip*
      OR engagement*
      OR democratic*
      OR coproduct*
      OR transdisc*
      OR multiactor
      OR "multi-actor"
      OR integrat*

    s_ch1_05: >-
      evaluat*
      OR reflex*
      OR reflect*
      OR monitor*
      OR adapt*
      OR learn*

    s_1_ch1_06: >-
      responsib*
      OR accountab*
      OR rights
      OR steward*
      OR reciproc*
      OR interdependen*
      OR (
          relation*
          OR plural
          OR divers*
          OR "sustainability-aligned"
          OR (
              care
              AND (
                  value*
                  OR ethic*
              )
          )
      )      
    
    s_1_ch2: >-
      vision
      OR future
      OR visionar*
      OR scenarios
      OR imagination
      OR imager*
      OR creativity
      OR desire
      OR wish*
      OR "visioning"
      OR "process"
      OR "participaory process*"
      OR "deliberate process*"
      OR "polic*"
      OR "target"
      OR "view*"
      OR "value"
      OR "cosmovision"
      OR "cosmocentric"
      OR "dream*"
      OR "fiction"
      OR "hope"
      OR "mission"
      OR "objective"
      OR "stORy"
      OR "wORldview*"
      OR "aspiration*"
      OR "action"
      OR "plan*"
      OR "strateg*"
      OR "intention"
      OR "model*"
      OR "solution*"
      OR "innovation*"
      OR "perspective"
      OR "platfORm"
      OR "collective action"
      OR "cooperation"
      OR "consultation"
      OR "coalition*"
      OR "response"
      OR "movement"
      OR "effORt"
      OR "initiative"
      OR "activity"
      OR "reaction"
      OR "perfORmance"
      OR "operation"
      OR "effect*"
      OR "task"
      OR "project"
      OR "influence" o "moment"
      OR "discourse"
      OR "motivation"
      OR "iteration"
      OR "roadmap"
      OR "agenda"
      OR "project"
      OR "programm"
      OR "government"
      OR "technique"
      OR "inspiration"
      OR "culture"
      OR "universe*"
      OR "reality"
      OR "fantasy"
      OR "perception"
      OR "visualization"
      OR "approach"
      OR "image"
      OR "arquetype"
      OR "existence"
      OR "cosmolog*"
      OR "co-production"
      OR "knowledge"
      OR "dialogue"
      OR "transmission"
      OR "conceptual*"
      OR "ceremon*"
      OR "relationships"
      OR "respect"
      OR "reciprocity"
      OR "responsibilities"
      OR "solidarity"
      OR "harmony"
      OR "self-determination"
      OR "communit*"
      OR "spiritual*"
      OR "languague"
      OR "territORy"
      OR "oppORtunit*"
      OR "sight"
      OR "fOResight"
      OR "idea"
      OR "appearance"

    s_1_ch3_01: >-
      Technolog*
      OR Science*
      OR "science-society"
      OR science-technology
      OR Solution

    s_1_ch3_02: >-
      "co-create"
      OR "co-creation"
      OR solution*
      OR knowledge*
      OR system*
      OR "t-lab*"
      OR "technology laboratory"
      OR educat*
      OR "socio-technic*"

    s_1_ch3_03: >-
      System*
      OR pathways
      OR connect*
      OR Agroecolog*
      OR Institutional
      OR Institutions
      OR Government*

    s_1_ch3_04: >-
      inner
      OR Personal
      OR Religio*
      OR Love
      OR Lov*
      OR Feelings
      OR Stewardship
      OR Care
      OR Beliefs
      OR Belie*
      OR Awareness
      OR "Self-Awareness"

    s_1_ch3_05: >-
      Worldviews
      OR Grassroot*
      OR "Community-based"
      OR Indigenous
      OR Leadership
      OR "Critical Science"
      OR Econfeminism
      OR "Political Ecology"
      OR Power
      OR Agency
      OR Environment*

    s_1_ch3_06: >-
      Economi*
      OR "Political Economy"
      OR institution*
      OR institutions      
      OR govern*
      OR econom*
      OR governance
      OR governm*
      OR globalization
      OR states
      OR colonial
      OR coloniali*
      OR labour
      OR organization*


    s_1_ch4_01: >-
      (
          challenge*
          OR barrier*
          OR obstacle*
          OR hinder*
          OR hindrance*
          OR block*
          OR prevent*
          OR deter*
          OR inertia*
          OR "path dependence*"
          OR "path dependency*"
          OR stasis*
          OR "lock-in*"
          OR trap*
          OR habits*
          OR habitual*
          OR "status quo*"
          OR power*
          OR "limiting factOR*"
      )
      AND (
          economic inequality
          OR Wealth concentration
          OR Socioeconomic inequality
          OR financialization
          OR uneven development
          OR Financialization
          OR Structural adjustment
          OR Sovereign Debt
          OR inequality
          OR Policy effectiveness
      )

    s_1_ch4_02: >-
      (
          challenge*
          OR barrier*
          OR obstacle*
          OR hinder*
          OR hindrance*
          OR block*
          OR prevent*
          OR deter*
          OR inertia*
          OR path dependence*
          OR path dependency*
          OR stasis*
          OR lock-in*
          OR trap*
          OR habits*
          OR habitual*
          OR status quo*
          OR power*
          OR "limiting factor*"
      )
      AND (
          "clean technolog*"
          OR "clean innovation*"
          OR "sustainable innovation"
          OR "sustainable technological innovation*"
      )
      AND (
          "limited access"
          OR "limited availability"
          OR "lack of access"
          OR "unavailability"
      )
     
    s_1_f_ch5_01: !expr function(){params$s_vision}

    s_f_ch5_02: !expr function(){paste0("(", params$s_vision, ") AND (", params$s_case, ")")}

    s_1_vision: >- 
      vision
      OR future
      OR visionar*
      OR scenarios
      OR imagination
      OR imager*
      OR creativity
      OR desire
      OR wish*
      OR visioning
      OR process
      OR "participatory process*"
      OR "deliberate process*"
      OR polic*
      OR target
      OR view*
      OR value
      OR cosmovision
      OR cosmocentric
      OR dream*
      OR fiction
      OR hope
      OR mission
      OR objective
      OR story
      OR worldview*
      OR aspiration*
      OR action
      OR plan*
      OR strateg*
      OR intention
      OR model*
      OR solution*
      OR innovation*
      OR perspective
      OR platform
      OR "collective action"
      OR cooperation
      OR consultation
      OR coalition*
      OR response
      OR movement
      OR effort
      OR initiative
      OR activity
      OR reaction
      OR performance
      OR operation
      OR effect*
      OR task
      OR project
      OR influence
      OR moment
      OR discourse
      OR motivation
      OR iteration
      OR roadmap
      OR agenda
      OR project
      OR programm
      OR government
      OR technique
      OR inspiration
      OR culture
      OR universe*
      OR reality
      OR fantasy
      OR perception
      OR visualization
      OR approach
      OR image
      OR arquetype
      OR existence
      OR cosmolog*
      OR co - production
      OR knowledge
      OR dialogue
      OR transmission
      OR conceptual*
      OR ceremon*
      OR relationships
      OR respect
      OR reciprocity
      OR responsibilities
      OR solidarity
      OR harmony
      OR self - determination
      OR communit*
      OR spiritual*
      OR languague
      OR territory
      OR opportunit*
      OR sight
      OR foresight
      OR idea
      OR appearance
      
    s_1_case: >-
      "case study*"
      OR case
      OR "study area*"
      OR example*
      OR evaluation
      OR concrete
      OR empirical
      OR practical
      OR initiative*
   
    concept_cuttoff: 0.6

    key_papers:
      - "./key papers/Ch 1 - Arun.csv"
      - "./key papers/Ch 2 - Sebastian.csv"
      - "./key papers/Ch 5 - Hannah.csv"
      - "./key papers/Ch 5 - Victoria.csv"

    mc.cores: 8
---

# Working Title
TfC Ch 2 Vision

## Code repo

[Github - private](https://github.com/IPBES-Data/IPBES-TfC-Ch-2-Vision)

# Introduction
The following terminology is used:

- **R1** - the first round of the literature search, i.e. (R1-transform) AND (R1-nature) AND (R1-vision)
    - **R1-transform** results of R1 only using the Transform search term
    - **R1-transform VA** results of R1 only using the Transform search term from the Values Assessment
    - **R1-nature** results of R1 only using the Nature search term
    - **R1-vision** results of R1 only using the Vision search term
    - **R1-X** results of R1 using the X search term
- **R2** - the second round of the literature search, i.e. R1 AND (search term for Case)

```{r}
#| label: setup
#| include: false
#| 

if (!exists("params")){
    params <- rmarkdown::yaml_front_matter('~/Documents_Local/git/IPBES_data_tsu/Assessments/Transformative Change/IPBES_TFC_Ch2_Vision/Status.qmd')$params
}

library(openalexR)
library(dplyr)

library(knitr)
library(tictoc)

# Function to make the search strings compacter
compact <- function(x){
  x |>
    gsub(pattern = "\n", replacement = " ") |>
    gsub(pattern = "\\*", replacement = "") |>
    gsub(pattern = "\\s+", replacement = " ") |>
    gsub(pattern = "\\( ", replacement = "(") |>    
    gsub(pattern = " )", replacement = ")")
}

if (!require("IPBES.R")){
    install.packages("IPBES.R", repos = c("https://ipbes-data.r-universe.dev", "https://cloud.r-project.org"))
    if (!require("IPBES.R")){
        stop("Package `IPBES.R` is not available and could not be installed!")
    }

}

```

# Suggested New search strategy

The suggested search strategy is a combination of a keyword based search Results (see @key_papers_in_corpi) and a concepts based filter. The concepts terms are selected by using their score, i.e. all concepts with a score higher than {r params$concept_cuttoff} are used. Please see section @concepts_selected for the list of concepts.

```{r}
#| label: search_combined 
#| 

#' @title FUNCTION_TITLE
#' @description FUNCTION_DESCRIPTION
#' @param search PARAM_DESCRIPTION, Default: NULL
#' @param concepts character vector. The search will be done by using `AND`, Default: NULL
#' @param dois character vector. dois which should be filtered for. If 
#'   longer than 1, these are collapsed into an `OR`. Default: NULL
#' @param count_only PARAM_DESCRIPTION, Default: TRUE
#' @param verbose PARAM_DESCRIPTION, Default: FALSE
#' @param return_call PARAM_DESCRIPTION, Default: FALSE
#' @param results_per_doi PARAM_DESCRIPTION, Default: FALSE
#' @return OUTPUT_DESCRIPTION
#' @details DETAILS
#' @examples 
#' \dontrun{
#' if(interactive()){
#'  #EXAMPLE1
#'  }
#' }
#' @seealso 
#'  \code{\link[openalexR]{oa_query}}, \code{\link[openalexR]{oa_request}}
#' @rdname get_search_combined
#' @export 
#' @importFrom openalexR oa_query oa_request
get_search_combined <- function(
    search = NULL,
    concepts.id = NULL,
    dois = NULL,
    count_only = TRUE,
    verbose = FALSE,
    return_call = FALSE,
    results_per_doi = FALSE){

    if (length(concepts.id > 1)){
      concepts.id <- paste0(concepts.id, collapse = "|")
    }

    if (!results_per_doi){
      if (length(dois > 1)) {
        dois <- paste0(dois, collapse = "|")
      }
    }
    query <- lapply(
        dois,
        function(doi) {
            oa_query(
                search = search,
                filter = list(concepts.id = concepts.id, from_publication_date = "1980-01-01", to_publication_date = "2023-12-30"),
                doi = doi,
                verbose = verbose
            )
        }
    )
    names(query) <- dois

    if (return_call) {
        return(query)
    }

    result <- lapply(
        query,
        function(q) {
            result <- openalexR::oa_request(q, count_only = count_only, verbose = verbose)
            if (count_only) {
                result <- unlist(result)
            }
        }
    )
    if (count_only){
      result <- do.call(rbind, result) |>
        as.data.frame() 
      result <- result[1] |> 
      t() |>
      unlist()
    }
   
    return(result)
}
```

# Get and calculate Data
## Search Term Definition
### search_term_hits
```{r}
#| label: get_search_term_hits
#|

tic()
fn <- file.path(".", "data", "search_term_hits.rds")
if (!file.exists(fn)) {
    search_term_hits <-
        sapply(
            grep("s_1_", names(params), value = TRUE),
            function(stn) {
                message("getting '", stn, "' ...")
                if (grepl("_f_", stn)){
                  search <- params[[stn]]()
                } else {
                  search <- params[[stn]]
                }
                search <- compact(search)
                openalexR::oa_query(search = search) |>
                    openalexR::oa_request(count_only = TRUE) |>
                    unlist()
            }
        ) |>
        t() |>
        as.data.frame() |>
        dplyr::mutate(
            query = c(
                "In OA",
                "Transform",
                "Nature",
                "Ch1 01",
                "Ch1 02",
                "Ch1 03",
                "Ch1 04",
                "Ch1 06",
                "Ch2",
                "Ch3 01",
                "Ch3 02",
                "Ch3 03",
                "Ch3 04",
                "Ch3 05",
                "Ch3 06",
                "Ch4 01",
                "Ch4 02",
                "Ch5_01",
                "Vision",
                "Case"
            )
        ) |>
        dplyr::mutate(page = NULL, per_page = NULL) |>
        dplyr::mutate(count = formatC(count, format = "f", big.mark = ",", digits = 0)) |>
        dplyr::relocate(query, .before = count)
    saveRDS(search_term_hits, file = fn)
} else {
    search_term_hits <- readRDS(fn)
}
toc()
```


## Key Papers and Works

### key_papers
Key papers were selected by Sebastian, Victoria and Hannah. 

```{r}
#| label: get_key_papers
#| 
fn <- file.path(".", "data", "key_papers.rds")
if (!file.exists(fn)) {
  key_papers <- lapply(
    params$key_papers,
    function(fn){
      read.csv(fn) |>
      select(Author, Publication.Year, Title, Publication.Title, DOI) |>
      rename(Year = Publication.Year, Journal = Publication.Title) |>
      arrange(desc(Year))
    }
  )
  names(key_papers) <- params$key_papers |>
      basename() |>
      gsub(pattern = "\\.csv", replacement = "") |>
      gsub(pattern = " ", replacement = "") |>
      gsub(pattern = "-", replacement = "_")

  saveRDS(key_papers, file = fn)
} else {
  key_papers <- readRDS(fn)
}
```

### key_works

```{r}
#| label: key_works
#| 

fn_kw <- file.path(".", "data", "key_works.rds")
fn_kw_df <- file.path(".", "data", "key_works_df.rds")
if (!all(file.exists(fn_kw, fn_kw_df))) {
  key_works <- lapply(
    key_papers,
    function(kp) {
      dois <- kp |>
        select(DOI) |>
        filter(DOI != "") |>
        unlist() |>
        tolower() |>
        unique()
      openalexR::oa_query(doi = dois) |>
        openalexR::oa_request(count_only = FALSE)
    }
  )
  saveRDS(key_works, file = fn_kw)

  key_works_df <- lapply(
    key_works,
    oa2df,
    entity = "works"
  )
  saveRDS(key_works_df, fn_kw_df)
} else {
  key_works <- readRDS(file = fn_kw)
  key_works_df <- readRDS(fn_kw_df)
}
```

### key_works_concepts

```{r}
#| label: key_works_concepts
#| 

fn <- file.path(".", "data", "key_works_concepts.rds")
if (!file.exists(fn)) {
    key_works_concepts <- lapply(
        key_works_df,
        function(kw_df) {
            do.call(rbind, kw_df$concepts) |>
                # filter(score > params$concept_cuttoff) |>
                arrange(desc(score))
        }
    )
    saveRDS(key_works_concepts, file = fn)
} else {
    key_works_concepts <- readRDS(file = fn)
}
```

### key_works_hits

```{r}
#| label: key_works_hits
#| 

fn <- file.path(".", "data", "key_works_hits.rds")
if (!file.exists(fn)) {
  key_works_hits <- lapply(
    key_works_df,
    function(kw_df) {
      message("Getting one key paper set... ")
      dois <- kw_df |>
        select(doi) |>
        distinct() |>
        unlist() |>
        unique() |>
        tolower()

      kw_h <-  sapply(
            grep("s_1_", names(params), value = TRUE),
            function(stn) {
                message("getting '", stn, "' ...")
                if (grepl("_f_", stn)) {
                    search <- params[[stn]]()
                } else {
                    search <- params[[stn]]
                }
                search <- params[[stn]]
                search <- compact(search)
                get_count(search_term = search, dois = dois)
            }
        ) |>
        as.data.frame()

      kw_h <- cbind(
        kw_h,
        Total = rowSums(kw_h)
      ) |>
        mutate(Total = Total - 1)

      kw_h <- rbind(
        kw_h,
        colSums(kw_h)
      )

      rownames(kw_h)[[nrow(kw_h)]] <- "Total"
      return(kw_h)
    }
  )

  saveRDS(key_works_hits, file = fn)
} else {
  key_works_hits <- readRDS(file = fn)
}
```


# Results

## Key Papers
### Number of Hits per Search Term

```{r}
#| label: hits_per_search_term_table
search_term_hits |>
    knitr::kable(
      row.names = FALSE,
        caption = "Number of hits",
    )
```

### Key papers in different corpi {#key_papers_in_corpi}

Here we show the number of hits for the key papers in the different corpi. The columns are:

- **In_OA**: is paper in OpenAlex?
- **R1_tf**: Is paper in Transformatifa Change Chapter 2
- **R1_tf_Ch5** Is paper in Transformative Change Chapter 5?
- **R1_tf_ts5** Is paper in Transformative Change definition as derived by the TSU?
- **R1_nat** Is paper in Nature Chapter 2?
- **R1_nat_Ch5**:  Is paper in Nature Chapter 5?
- **R1_nat_VA**: Is paper in Nature as defined in the Values Assessment?
- **R1_vis**: Is paper in Vision Chapter 2?
- **Total**: Total number of hits per row

```{r}
#| label: key_paper_hits_in_corpi
#| 

tbl <- lapply(
    names(key_works_hits),
    function(n) {
        kwh <- key_works_hits[[n]]
        total <- grepl("Total", rownames(kwh))
        rownames(kwh)[!total] <- paste0(n, " - <a href='https://doi.org/", rownames(kwh)[!total], "' target='_blank'>Click here</a>")
        rownames(kwh)[total] <- paste0("**", n, " - Total**")
        kwh |>
            arrange(Total) |>
            apply(
                c(1, 2),
                function(x) {
                    ifelse(x == 0, "<font color='red'>0</font>", paste0("<font color='green'>", x, "</font>"))
                }
            ) |>
            as.data.frame()
    }
) |>
    do.call(what = rbind)

detail <- rbind(
    "**overall**" = paste0(
        "**",
        c(
            search_term_hits |>
                slice(c(1:6, 8:9)) |>
                select(count) |>
                unlist() |>
                as.vector(),
            ""
        ),
        "**"
    ),
    tbl
)

```

### Key Papers in corpi based on new search strategy



```{r}
#| label: TMP_search_combined_test
#| eval: false

ids <- key_works_concepts |>
  do.call(what = rbind) |>
  filter(level == 0) |>
  arrange(desc(score)) |>
  distinct(id, .keep_all = TRUE) |>
  select(display_name) |>
  # slice(1:50) |>
  unlist() |>
  as.vector() |> unique()


dois <- key_works_df |>
  do.call(what = rbind) |>
  select(doi) |>
  unlist() |>
  unique() |>
  as.vector()



get_search_combined(
  # search = paste0( "(", params$s_tsf_comb, ")" ),
  search = paste0( "(", params$s_tsf_comb, ") AND (",  params$s_nat_rev, ")" ),
  concepts.id = paste0(ids, collapse = "|"),
#  dois = dois,
  count_only = TRUE,
  verbose = TRUE
)

openalexR::oa_query(concepts.id = "https://openalex.org/c86803240|https://openalex.org/c39432304") |>
  openalexR::oa_request(count_only = TRUE) |>
  unlist()

x <- (openalexR::oa_query(doi = key_papers) |> openalexR::oa_request(count_only = FALSE) |> oa2df(entity = "works"))
```



#### Summary
```{r}
in_summary <- grepl("Total|overall", rownames(detail))
knitr::kable(detail[in_summary,])
```

#### Detail
```{r}
knitr::kable(detail)
```

## Search Terms
### Differences Transformative Change terms

### Differences Nature terms

### Vision Terms

### Case Study Terms

## Detailed Search Terms

### [About Transformative change] Transformative change synonyms




# TODO

- Transformative Change Query term identical between chapters 2 and 5
- Nature Query terms identical between chapters between chapters 2 and 5
- 

- Randomly 100 papers from R1
- add large number of articles to Zotero
- all open acces articles only for now.

## R3
- get all pdfs which are available from R3
- Results, Discussion and Conclusion - Vision, geograph, country name, words from transformative change

# ==== APPENDIX ====


## Results WoS

### R1

[R1 WoS](https://www.webofscience.com/wos/alldb/summary/9cc620dd-dfc6-4414-acc0-983d4a56314c-a1bdf5a4/relevance/1)

1,237,718 hits

### R2

AND ('case stud*' OR 'case' OR 'study area*' OR 'example*' OR 'evaluation' OR 'concrete' OR 'empirical', OR 'practical' OR 'initiative*')

[R2 WoS](https://www.webofscience.com/wos/alldb/summary/f6d3094a-0cc2-4662-9b05-0a671c71c86a-a1be094a/relevance/1)

296,551 hits, i.e. about 1,100,000 without case studies
```